---
title: "H1-Draft 1"
author: "HG"
date: "16/8/2021"
output: pdf_document
---


```{r include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr) # To show formatted tables (kable).
```

\begin{center}

\vspace{14mm}  
  
\LARGE 
Universidad de Monterrey
  
\vspace{3mm}  
  
\Large Econometría de Mercados Financieros
  
\vspace{30mm}  
  
\huge Homework 1
  
\vspace{30mm}   
  
\Large Dr. Martín Carlos Lozano Banda  
  

\end{center}

\vspace{25mm}  
  
\Large   
 Héctor Misael González Valerio  
  Sergio Octavio Castro Cobos  
  Mariana Ocañas Zapata  
  Samantha Valdez Güereca 
  
\vspace{0.08mm}

\Large
  Paulina Cárdenas Rodríguez
  
\vfill

\begin{center}
San Pedro Garza García, N.L. August 30th, 2021
\end{center}

\newpage


# Introduction

```{r, include = false} 
# Load libraries
library(h2o)
library(timetk)
library(tidyquant)
library(dplyr)
library(ggplot2)
library(tibble)
library(kableExtra)
library(knitr)
library(bit64)
library(sweep)
library(forecast)
```

# Forecasting techniques

## H2O Machine Learning
## Linear Regression
## ARIMA

# Results

# Conclusions

# References

# Honor Code

We hereby declare that we have done this assignment with academic integrity
